Compressive Channel Sensing of Multipath Millimeter Channel via a Beamspace Dantzig Selector and its Probabilitic Performance Bound

### 2019-01-08 ongoing/report/sec_1_introduction.tex
Finish the Main Bound

\Result
{Definition}
{
Consider \(P \in \MB{M}_{\MB{K}} (N_m, N_p)\), with unity-\(\ell_2\)-norm columns.
For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the RIP of order \(s\) with respect to parameter \(0 \leq \delta_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq s\), for all \(\MC{T} \subset T(N_m)\) with \(|\MC{T}| \leq s\),
%
\Disp{
(1-\delta_s) \|h\|^2
\leq \|P_{\MB{T}} h\|_2^2
\leq (1+\delta_s) \|h\|^2
}
}

RIP of order \(s\) is essentially saying that the matrix \(X\) is ``almost unitary'' up to ``relative error'' \(\delta_s\).

@@

The constant \(\delta\) in the proof of DS is significant.
Indeed, we may observe that in theorem (), the bound is not tightest when \(\delta=0\), i.e., that \(P\) is fully unitary, rendering the RIP an important role.
Here, it is not clear at first what matrices serves as the RIP condition.

@@

\Result
{Theorem}
{
Let each entry of random matrix \(P \in \MB{M}_\MB{K} (N_m, N_p)\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\sqrt{N_m}\) (that is, Rademacher distribution).
Then, with \(0 <\epsilon <1\),
%
\Disp{
\MB{P} ( |\|P h\|_2^2 -\|h\|_2^2| \geq \epsilon \|h\|_2^2)
\leq 2 \exp (-n (\epsilon^2/4 -\epsilon^3/6) )
}
}

@@

\Result
{Theorem}
{
Following the setting described above, suppose, for \(0 <\delta <1\),
%
\Disp{
M \geq 16s \log (N/\delta)
}
%
Then OMP (Algorithm \_\_) recovers \(x\) completely, with overwhelming probability \(1-\delta\).
}

>>>>

\Result
{Definition}
{
Consider \(P \in \MB{M}_{\MB{K}} (N_m, N_p)\), with unity-\(\ell_2\)-norm columns.
For \(s =1, \dotsc N_p\), we say that \(P\) satisfies the RIP of order \(s\) with respect to parameter \(0 \leq \d_S \leq 1\), if, for all \(x\) with \(\|x\|_0 \leq s\), for all \(\MC{T} \subset T(N_m)\) with \(|\MC{T}| \leq s\),
%
\Disp{
(1-\d_s) \|h\|^2
\leq \|P_{\MB{T}} h\|_2^2
\leq (1+\d_s) \|h\|^2
}
}

RIP of order \(s\) is essentially saying that the matrix \(X\) is ``almost unitary'' up to ``relative error'' \(\d_s\).

@@

The constant \(\d\) in the proof of DS is significant.
Indeed, we may observe that in theorem (), the bound is not tightest when \(\d=0\), i.e., that \(P\) is fully unitary, rendering the RIP an important role.
Here, it is not clear at first what matrices serves as the RIP condition.

@@

\Result
{Theorem}
{
Let each entry of random matrix \(P \in \MB{M}_\MB{K} (N_m, N_p)\) be defined as i.i.d.\ Bernoulli with value \(\pm 1/\R{N_m}\) (that is, Rademacher distribution).
Then, with \(0 <\epsilon <1\),
%
\Disp{
\MB{P} ( |\|P h\|_2^2 -\|h\|_2^2| \geq \epsilon \|h\|_2^2)
\leq 2 \exp (-n (\epsilon^2/4 -\epsilon^3/6) )
}
}

@@

\Result
{Theorem}
{
Following the setting described above, suppose, for \(0 <\d <1\),
%
\Disp{
M \geq 16s \log (N/\d)
}
%
Then OMP (Algorithm \_\_) recovers \(x\) completely, with overwhelming probability \(1-\d\).
}

### 2019-01-08 ongoing/report/sec_2_problem_setting.tex
Finish the Main Bound

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
%
\Disp{
H
=\sum_{l=1}^L \alpha_l \V{a} \left( \F{d} {\lambda} \sin \varphi_l' \right) \V{a} \left( \F{d_{\RM{arr}}} {\lambda} \sin \vartheta_l' \right)^\H
}
%
The physical meaning of \(\vartheta_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\vartheta_l\), the \(l\)-th that of arrival wave, while \(d_{\RM{arr}}\) is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \(\V{a}\) as
%
\Disp{
\varphi_l
=\F{d_{\RM{arr}}} {\lambda} \sin \varphi_l' \\
\vartheta_l
=\F{d_{\RM{arr}}} {\lambda} \sin \vartheta_l'
}
%
to get a simpler form
%
\Disp{
H
=\sum_{l=0}^L \alpha_l \V{a} (\varphi_l) \V{a} (\vartheta_l)^\H
}
%

@@

Introduce the discrete Fourier matrix \(\M{K}\) defined to be
%
\Disp{
\M{K} \in &\MB{M}_{\MB{C}} (N_H, N_H) \NT \\
\M{K} (n_1, n_2) =&\F{1} {\sqrt{N_H}} \RM{e}^{2\pi i n_1 n_2 /N_H}, \\
\quad n_1, n_2 =&0, 1, \dotsc, N_H-1 \NT
}
%
Observe that, if we write
%
\Disp{
\M{G}
=\M{K}^\H \M{H} \M{K}
}
%
which has the interpretation as the beamspace (i.e., spatial frequency domain) representation of \(\M{H}\), then
%
\Disp{
\M{Y}
:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{K}^\H \M{F}_R \M{F}_B +\M{K}^\H \M{Z} )
}
%
If at the end of day, \(\M{G}\) is sparse, then we recover \(\M{G}\) instead, and our use of DS is fully justified.

>>>>

And consider the virtual representation of the MIMO channel (see for example Akdeniz et.\ al.\ 2014).
%
\Disp{
H
=\sum_{l=1}^L \alpha_l \V{a} \left( \F{d} {\lambda} \sin \f_l' \right) \V{a} \left( \F{d_{\RM{arr}}} {\lambda} \sin \th_l' \right)^\H
}
%
The physical meaning of \(\th_l\) is the \(l\)-th angle of incidence (formed by the ray and the normal line) of departure electronic wave, and \(\th_l\), the \(l\)-th that of arrival wave, while \(d_{\RM{arr}}\) is the distance between two adjacent antennae.
For our purpose, we may absorb the argument of \(\V{a}\) as
%
\Disp{
\f_l
=\F{d_{\RM{arr}}} {\lambda} \sin \f_l' \\
\th_l
=\F{d_{\RM{arr}}} {\lambda} \sin \th_l'
}
%
to get a simpler form
%
\Disp{
H
=\sum_{l=0}^L \alpha_l \V{a} (\f_l) \V{a} (\th_l)^\H
}
%

@@

Introduce the discrete Fourier matrix \(\M{K}\) defined to be
%
\Disp{
\M{K} \in &\MB{M}_{\MB{C}} (N_H, N_H) \NT \\
\M{K} (n_1, n_2) =&\F{1} {\R{N_H}} \RM{e}^{2\pi i n_1 n_2 /N_H}, \\
\quad n_1, n_2 =&0, 1, \dotsc, N_H-1 \NT
}
%
Observe that, if we write
%
\Disp{
\M{G}
=\M{K}^\H \M{H} \M{K}
}
%
which has the interpretation as the beamspace (i.e., spatial frequency domain) representation of \(\M{H}\), then
%
\Disp{
\M{Y}
:=\M{W}_B \M{W}_R \M{K} ( \M{G} \M{K}^\H \M{F}_R \M{F}_B +\M{K}^\H \M{Z} )
}
%
If at the end of day, \(\M{G}\) is sparse, then we recover \(\M{G}\) instead, and our use of DS is fully justified.

### 2019-01-08 ongoing/report/sec_3_theorems_and_proofs.tex
Finish the Main Bound

We apply DS to find \(\hat{g}\), setting
\Disp{
\gamma =\sqrt{2 \log N_g}
}
Other values are of course possible, but this is enough to illustrate our purpose.
Also set for short
%
\Disp{
d =\hat{g} -g
}
%
And call
\begin{itemize}
\item \(\MC{A}\) be the largest \(s\) position of \(g\).
\item \(\MC{B}\) be the largest \(s\) position of \(d_{T(N_g) -\MC{A}}\).
\item \(\MC{C} =T(N_g) -\MC{A}\), i.e., the complementary index set of \(\MC{A}\).
\end{itemize}

@@

\Result
{Lemma (Tentative)}
{
Suppose \(0 \leq \varphi \leq 2\pi k /N_H\), \(k =0, \dotsc, N_H-1\).
Let \(\varphi\) be given, and array response \(\V{a} (\varphi)\) defined as in ().
Then \(\V{a} (\varphi)\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R\)
%
\Disp{
R
\leq 2 N_H \log \F{2\pi N_H}{L}.
}
}

The lemma is the key to estimating sparsity of \(h\), which we now show.
Recall the identity for Dirichlet kernel
%
\Disp{
D (\varphi')
:=&\left| \sum_{n=0}^{N_H-1} \RM{e}^{i n \varphi'} \right| \NT \\
=&\F{|\sin (N_H \varphi'/2)|}{|\sin (\varphi' /2)|},
\quad 0 \leq \varphi' \leq \pi
}
%
And recall the Taylor expansion of sin for the first two terms with respect to zero
%
\Disp{
\sin x =x -\F{x^3}{6} + \MC{O}(x^5), \quad x \ll 1
}
%
Actually it can be shown that we have a inequality
%
\Disp{
\left| x -\F{x^3}{6} \right| \leq \sin x, \quad -\pi \leq x \leq \pi
}
%
Applying the above inequality to the denominator and bounding the nominator by 1, we have
%
\Disp{
\left| D (\varphi') \right|
= \F{48}{|\varphi'^2 -24| |\varphi'|}
\quad 0 \leq \varphi' \leq \pi,
}

Particularly, for arbitrary \(\varphi\), find \(k\) so that
\Disp{
\eta :=&\varphi -\F{2\pi k}{N_H}, \\
\left| \eta \right|
\leq &\F{2\pi}{N_H}.
}
%
Then observe
\Disp{
K^\H a(\varphi) (k)
=D \left( \varphi -\F{2 \pi k} {N_H} \right)
}
So we need only bound
\Disp{
R(\eta) :=\sum_{n_H =s}^{N_H -1} D \left( \eta +\F{2 \pi n_H} {N_H} \right)
}
By the approximation of rectangle to integral,
\Disp{
R(\eta) -\F{2\pi} {N_H}
\leq N_H \int_{\varphi'=2\pi L/N_H}^{2\pi} |D(\varphi')| d \varphi'
}
Bound \(D\) by above technique, meanwhile we notice \(\varphi' <24\).
\Disp{
R(\varphi)
\leq &\F{N_H}{2\pi} \int_{\varphi'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\varphi'^2) \varphi'} d \varphi'
+\F{2\pi} {N_H} \\
=&\F{N_H}{\pi} \log \F{2\pi N_H}{L} -\log \F{4\pi^2 -24} {L^2/N_H^2 -24}
+\F{2\pi} {N_H}
}
Notice the second log term \(<1\) and we drop that.
Also drop \(2\pi /N_H\) since it is small.
Furthermore the \(2\pi\) factor in log can be dropped too.
\Disp{
R(\varphi)
\leq \F{N_H}{\pi} \log \F{N_H}{L}.
}

\Result
{Lemma (Tentative)}
{
Let \(\varphi\) and \(\vartheta\) be uniformly, independently distributed in \([0,2\pi)\), and linear array response \(\V{a}\) defined as in ().
Let \(g\) be defined as above.
Then \(g\) is almost-\(L\)-sparse with \(\ell_1\)-residue
%
\Disp{
R
\leq \F{L N_H^2}{\pi^2} \left( \log \F{N_H}{L} \right)
}
}

@@

\Result
{Lemma}
{
Let \(P\) be given.
Then \(\tau_{s, s'}\) is bounded in both direction as follows,
\Disp{
\delta_{s+s'} -\max (\{\delta_s, \delta_{s'}\})
\leq \tau_{s, s'}
\leq \delta_{s+s'}
}
}

Thus \(\delta_s\), which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
We may well keep track of \(\delta_s\) only.

\Result
{Lemma}
{
Let \(P\) be i.i.d.\ Radmacher, as defined in Lemma ().
Then \(P\) is RIP according to \(\delta\) for at least probability
\Disp{
   1 -2 \left( \F{12}{\delta} \right)^s \exp \left[ - \left( \F{\epsilon^2}{4} -\F{\epsilon^3}{6} \right) \F{\delta}{2} N_p \right]
}
}

@@

\Result
{Lemma}
{
Let \(z\) and \(P\) be defined as above.
Then
%
\Disp{
|\IP{ z, P(:, n_g) }|
\leq& 2 \sqrt{\log N_g},
\quad n_g =1, \dotsc, N_g.
}
%
with overwhelming probability.
}

@@

\Result
{Lemma}
{
Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in ().
%
\Disp{
\|P^\H P d\|_\infty
\leq& 4 \sqrt{\log N_g},
\quad n_g =1, \dotsc, N_g.
}
}

@@

By construction
\Disp{
\| P (:,n_y)^\H (y -P \hat{g}) \|
\leq &\| P^\H (y -P \hat{g}) \|_\infty \\
\leq &2\sqrt{\log N_g}
}
By triangle inequality, together with lemma (), we have
\Disp{
\|P (:,n_y)^\H P d\|
\leq &\|\IP{ z, P (:,n_y) }\| +\IP{ y -P \hat{g}, P (:,n_y) } \\
\leq &2 \sqrt{\log N_g} +2 \sqrt{\log N_g}
}
which implies
\Disp{
\|P^\H P d\|_\infty
\leq &4 \sqrt{\log N_g}.
}

@@

\Result
{Lemma}
{
Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in () with respect to \(\delta_s\).
%
\Disp{
\|d_{\MC{AB}}\|_2
\leq \F{1}{1-\delta_{2s}} \|P_{\MC{A}\MC{B}}^\Tr P d\|_2 +\F{\delta_{3s}}{(1-\delta_{2s}) \sqrt{L}} \|d_{C}\|_1
}
%
}

@@

\Result
{Theorem}
{
Let \(y\), \(P\), \(g\), \(\hat{g}\), \(d\) be defined as above.
Then, if \(g\) is almost-\(L\)-sparse with residue \(\epsilon(N,L)\), then
\Disp{
-\|g_{\MC{C}}\|_2
\leq C 4 (\log N_g) \cdot \left( L +\F{1}{L} \epsilon(N,L) \right)
}
with overwhelming probability.
}

\Disp{
\| d \|_2^2
\leq &\|d_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|d_{\MC{C}}\|_1^2 \\
\leq \F{1}{(1-\delta_{2s})^2}
\left(
\|P_{\MC{A}\MC{B}}^\Tr P d\|_2^2
+\F{\delta_{3s}^2} {(1-\delta_{2s})^2 L} \|d_{C}\|_1^2
\right)
+\F{1}{L} \|d_{\MC{C}}\|_1^2
}

>>>>

We apply DS to find \(\hat{g}\), setting
\Disp{
\gamma =\R{2 \log N_g}
}
Other values are of course possible, but this is enough to illustrate our purpose.
Also set for short
%
\Disp{
d =\hat{g} -g
}
%
And call
\begin{itemize}
\item \(\MC{A}\) be the largest \(s\) position of \(g\).
\item \(\MC{B}\) be the largest \(s\) position of \(d_{T(N_g) -\MC{A}}\).
\item \(\MC{C} =T(N_g) -\MC{A}\), i.e., the complementary index set of \(\MC{A}\).
\end{itemize}

@@

\Result
{Lemma (Tentative)}
{
Suppose \(0 \leq \f \leq 2\pi k /N_H\), \(k =0, \dotsc, N_H-1\).
Let \(\f\) be given, and array response \(\V{a} (\f)\) defined as in ().
Then \(\V{a} (\f)\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
%
\Disp{
R
\leq 2 N_H \log \F{2\pi N_H}{L}.
}
}

The lemma is the key to estimating sparsity of \(h\), which we now show.
Recall the identity for Dirichlet kernel
%
\Disp{
D (\f')
:=&\left| \sum_{n=0}^{N_H-1} \RM{e}^{i n \f'} \right| \NT \\
=&\F{|\sin (N_H \f'/2)|}{|\sin (\f' /2)|},
\quad 0 \leq \f' \leq \pi
}
%
And recall the Taylor expansion of sin for the first two terms with respect to zero
%
\Disp{
\sin x =x -\F{x^3}{6} + \MC{O}(x^5), \quad x \ll 1
}
%
Actually it can be shown that we have a inequality
%
\Disp{
\left| x -\F{x^3}{6} \right| \leq \sin x, \quad -\pi \leq x \leq \pi
}
%
Applying the above inequality to the denominator and bounding the nominator by 1, we have
%
\Disp{
\left| D (\f') \right|
= \F{48}{|\f'^2 -24| |\f'|}
\quad 0 \leq \f' \leq \pi,
}

Particularly, for arbitrary \(\f\), find \(k\) so that
\Disp{
\eta :=&\f -\F{2\pi k}{N_H}, \\
\left| \eta \right|
\leq &\F{2\pi}{N_H}.
}
%
Then observe
\Disp{
K^\H a(\f) (k)
=\F{1}{N_H} D \left( \f -\F{2 \pi k} {N_H} \right)
}
So we need only bound
\Disp{
R(\eta)
:=\F{1}{N_H} \sum_{n_H =s}^{N_H -1} D \left( \eta +\F{2 \pi n_H} {N_H} \right)
}
By the approximation of rectangle to integral,
\Disp{
R(\eta) -\F{2\pi} {N_H}
\leq \F{1}{N_H} N_H \int_{\f'=2\pi L/N_H}^{2\pi} |D(\f')| d \f'
}
Bound \(D\) by above technique, meanwhile we notice \(\f' <24\).
\Disp{
R(\f)
\leq &\F{1}{2\pi} \int_{\f'=2\pi L/N_H}^{2\pi} \F{48}{(24 -\f'^2) \f'} d \f'
+\F{2\pi} {N_H} \\
=&\F{1}{\pi} \log \F{2\pi N_H}{L}
-\F{1}{N_H} \log \F{4\pi^2 -24} {L^2/N_H^2 -24}
+\F{2\pi} {N_H}
}
Notice the argument of log in the second term \(<1\), and we drop that.
Also drop \(2\pi /N_H\) since it is small.
Furthermore the \(2\pi\) factor in log can be dropped too.
\Disp{
R(\f)
\leq \F{1}{\pi} \log \F{N_H}{L}.
}

\Result
{Lemma (Tentative)}
{
Let \(\f\) and \(\th\) be uniformly, independently distributed in \([0,2\pi)\), and linear array response \(\V{a}\) defined as in ().
Let \(g\) be defined as above.
Then \(g\) is almost-\(L\)-sparse with \(\ell_1\)-residue \(R(N_H, L)\) to be
%
\Disp{
R
\leq \F{L}{\pi^2} \left( \log \F{N_H}{L} \right)^2
}
}

@@

\Result
{Lemma}
{
Let \(P\) be given.
Then \(\tau_{s, s'}\) is bounded in both direction as follows,
\Disp{
\d_{s+s'} -\max (\{\d_s, \d_{s'}\})
\leq \tau_{s, s'}
\leq \d_{s+s'}
}
}

Thus \(\d_s\), which defines how much the deformation of norm is, also tells us how much the inner product is deformed.
We may well keep track of \(\d_s\) only.

\Result
{Lemma}
{
Let \(P\) be i.i.d.\ Radmacher, as defined in Lemma ().
Then \(P\) is RIP according to \(\d\) for at least probability
\Disp{
   1 -2 \left( \F{12}{\d} \right)^s \exp \left[ - \left( \F{\epsilon^2}{4} -\F{\epsilon^3}{6} \right) \F{\d}{2} N_p \right]
}
}

@@

\Result
{Lemma}
{
Let \(z\) and \(P\) be defined as above.
Then
%
\Disp{
|\IP{ z, P(:, n_g) }|
\leq& 2 \R{\log N_g},
\quad n_g =1, \dotsc, N_g.
}
%
with overwhelming probability.
}

@@

\Result
{Lemma}
{
Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in ().
%
\Disp{
\|P^\H P d\|_\infty
\leq& 4 \R{\log N_g},
\quad n_g =1, \dotsc, N_g.
}
}

@@

By construction
\Disp{
\| P (:,n_y)^\H (y -P \hat{g}) \|
\leq &\| P^\H (y -P \hat{g}) \|_\infty \\
\leq &2\R{\log N_g}
}
By triangle inequality, together with lemma (), we have
\Disp{
\|P (:,n_y)^\H P d\|
\leq &\|\IP{ z, P (:,n_y) }\| +\IP{ y -P \hat{g}, P (:,n_y) } \\
\leq &2 \R{\log N_g} +2 \R{\log N_g}
}
which implies
\Disp{
\|P^\H P d\|_\infty
\leq &4 \R{\log N_g}.
}

@@

\Result
{Lemma}
{
Let \(d\) and \(P\) be defined as above, and \(P\) satisfies RIP as in () with respect to \(\d_s\).
%
\Disp{
\|d_{\MC{AB}}\|_2
\leq \F{1}{1-\d_{2L}} \|P_{\MC{A}\MC{B}}^\Tr P d\|_2 +\F{\d_{3L}}{(1-\d_{2L}) \R{L}} \|d_{C}\|_1
}
%
}

@@

\Result
{Theorem}
{
Let \(y\), \(P\), \(g\), \(\hat{g}\), \(d\) be defined as above.
Then
\Disp{
\|d\|_2
\leq \F{4 L^4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) ( \log N_H )^4
}
with overwhelming probability.
}

We are ready to combine previous lemmata.
The first quantity we want to bound away is
\Disp{
\|P_{\MC{A}\MC{B}}^\Tr P d\|_2
\leq &\|P^\Tr P d\|_2 \NT \\
\leq &\R{N_g} \|P^\Tr P d\|_\infty \NT \\
\leq &4 \R{ N_g \log N_g }
}
Thus, by virtue of Lemma (),
\Disp{
\| d_{A} \|_1
\leq &\R{L} \| d_{A} \|_2 \NT \\
\leq &\R{L} \| d_{\MC{AB}} \|_2 \NT \\
\leq &\F {\d_{3L}} {1-\d_{2L}} \| d_{\MC{C}} \|_1 +\F {4} {1-\d_{2L}} \R{L N_g \log N_g} 
}

As the next step, we must eliminate \(\|d_{\MC{A}}\|_1\) in rhs of Lemma ().
\Disp{
\| d_{\MC{C}} \|_1
\leq &\| d_{\MC{A}} \|_1 +2 \| g_{\MC{C}} \|_1 \NT \\
\leq &\F {\d_{3L}} {1-\d_{2L}} \| d_{\MC{C}} \|_1
+2 \| g_{\MC{C}} \|_1
+\F {4} {1-\d_{2L}} \R{L N_g \log N_g}
}
Or,
\Disp{
\| d_{\MC{C}} \|_1
\leq &2 \F{1-\d_{2L}} {1 -\d_{2L} -\d_{3L}} \| g_{\MC{C}} \|_1
+\F {4} {1-\d_{2L} -\d_{3L}} \R{L N_g \log N_g}
}

We are ready to bound \(\| d \|_2^2\).
Using Lemma () again, we have
\Disp{
\| d \|_2^2
\leq &\|d_{\MC{A}\MC{B}}\|_2^2 +\F{1}{L} \|d_{\MC{C}}\|_1^2 \NT \\
\leq & \left( \F{\d_{3L}^2} {L^2 (1-\d_{2L})^2} +\F{1}{L} \right) \|d_{\MC{C}}\|_1^2
+\F{8 \d_{3L}} {L (1-\d_{2L})^2} \R{N_g \log N_g} \|d_{\MC{C}}\|_1 \NT \\
&\quad +\F{16}{(1-\d_{2L})^2} N_g \log N_g
}
Finally, plug in the bound for \(\|d_{\MC{C}}\|_1\), the last unknown, and we make use of the almost-sparsity condition of \(\|d_{\MC{C}}\|_1\).
There are several dozens of terms if we expand all.
but for simplicity, we keep only the leading term under the approximation
\Disp{
1 \ll L \ll N_g
}
And expand to the first order expressions containing \(\d_{2L}\) or \(\d_{3L}\) in the denominator using
\Disp{
\d_{2L} <\d_{3L} \ll 1.
}
Then
\Disp{
\|d\|_2^2
\leq \F{4 L^4}{\pi^4} \d_{3L}^4 (1-2\d_{2L}) ( \log N_H )^4
}
